Updates on the Exoplanet Orbit Database

### 2013-12-29 draft/ms.tex
Refine structure of paper: add subsections and section outlines. Update new_table_items.txt: REF and URL and misc.

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to Eunkyu Han at hek90625@gmail.com.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}

@@

Restrict the updates in this section on EOD updates.

Parameter updates, new table parameters etc. What other updates are there?

@@

%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}
These include:
OTHERNAME - This is now listed as other name of planet instead of star;
DISCMETH - replaced by planetdiscmeth and stardiscmeth;
S - changed to SHK;
SPSTAR - stellar type of star (unvetted), gone;
NSTEDID - replaced by EANAME (Exoplanet Archive).

@@

>>>>

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to datamaster@exoplanets.org.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}

@@

Restrict the updates in this section on EOD updates. We only report
new additions and revised fields here. For details on other fields,
see \cite{Wright2011}. We divide the fields into categories in
consistency with the interactive table on exoplanets.org. Some fields
are not explicitly included in the interactive table (e.g., the URLs), but are
explicitly listed in the downloadable {\tt .csv} file.\footnote{The
  entire dataset provided by exoplanets.org is available for download in a
  single CSV file at \url{http://exoplanets.org/csv-files/exoplanets.csv}}

%------------------------------------------------------------------------------
\subsection{Planet Information}

Added fields since \cite{Wright2011}:

KEPID

KOI

KDE

EOD

MICROLENSING, IMAGING, TIMING and ASTROMETRY

%------------------------------------------------------------------------------
\subsection{Stellar Parameters}

Added fields since \cite{Wright2011}:

DIST

GAMMA

%------------------------------------------------------------------------------
\subsection{Orbit Parameters}

Added fields since \cite{Wright2011}:

MASSS

SEP

BIGOM

%------------------------------------------------------------------------------
\subsection{Transit Parameters}

Added fields since \cite{Wright2011}:

DR

RR

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}

This is a entire new set of fields since \cite{Wright2011}:

SE

SEDEPTH J H KS KP 36 45 58 80

SET

%------------------------------------------------------------------------------
\subsection{Stellar Properties}

Difference from Stellar Parameters: these are derived parameters based
on spectroscopy and stellar models.
Added fields since \cite{Wright2011}:

RSTAR

RHOSTAR

KP

%------------------------------------------------------------------------------
\subsection{Uncertainties}

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower ZZZ 1$\sigma$ ZZZ
uncertainties, and they are different when the error bars are
asymmetric. UX contains the ZZZ 1$\sigma$ ZZZ uncertainty, and it
equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).

%------------------------------------------------------------------------------
\subsection{References}

Added field: ZZZ MONTH ZZZ, PLANETDISCMETH, STARDISCMETH.

The fields XREF and XURL store the peer-reviewed reference and link to
the publication for the field X. The following fields now have XREF
and XURL: (previously in \citealt{Wright2011}) DIST, TRANSIT, BINARY;
(new) fields in stellar parameters: V\footnote{ZZZ VREF and VURL are
  also for J, H, KS. ZZZ}, VSINI, GAMMA; all orbit pars except for
trend and freeze\_ecc; all transit parameters; all SE parameters;
fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.

Other general reference fields: In \cite{Wright2011}: FIRSTREF,
FIRSTURL, ORBREF, ORBURL. New: SPECREF, SPECURL contain source of most
of the spectroscopic parameters listed for convenience; actual
references in the REF fields take precedence over this one.

%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}

These include:

OTHERNAME - This is now listed as other name of planet instead of star;

DISCMETH - replaced by planetdiscmeth and stardiscmeth;

S - changed to SHK;

SPSTAR - stellar type of star (unvetted), gone;

NSTEDID - replaced by EANAME (Exoplanet Archive).

MASSREF, MASSURL - originally for stellar mass reference, now for planet mass.

@@

@@

We now include \kepler\ candidates...

We also include planets discovered microlensing, imaging, timing,
astrometric motion. Some microlensing and imaging planets are not
included in the EOD because of poorly characterized orbits...
